Online {\IterComp}

### 2017-11-16 results.tex
updates to result section

%Mean values...
%Real-R5: 30.43\%
%WPO-R5:  54.97\%
%adpcm_d:
%Real-R5: 75.51\%
%WPO-R5:  79.07\%

@@

\subsubsection{Analysis of the cost during the online search}

@@

A Search Driver based on genetic algorithm is able to focus the search on promising optimization sequences, reducing the risk of
executing sub-optimal versions of the program as the search evolves through generations.
Although the user may experience slowdown during the optimization process, due to overheads or by executing sub-optimal versions of the program, after the first generation,
the optimization sequences produced tend to overcome these costs, with their benefits surpassing the profiling overheads.

>>>>

@@

\subsubsection{Evaluation of the Costs During the Online Search}

@@

With online iterative optimization, although the 
user may experience slowdown during the search process by executing sub-optimal versions of the program,
a Search Driver based on genetic algorithm is able to focus the search on promising optimization sequences, reducing the risk of
executing sub-optimal versions of the program as the search evolves through generations.
After the first generation, the optimization sequences produced tend to overcome this issue, with their benefits surpassing the profiling overheads.
